Safe Transferable Regions

### 2015-11-13 paper/introduction.tex
Discussion of motivating example in BROOM
updates to intro

\newcommand{\TODO}[1]{\textbf{TODO: #1}}
\newcommand{\eg}{\emph{e.g.}}

@@

Consider the example shown in Fig.~\ref{fig:motivating-eg}.
This code represents the logic for a streaming query operator.
The operator receives a stream of input messages, each associated
with a time (window) $t$, processed by method \texttt{onReceive}.
Each input message contains a list of inputs, each of which is processed
by applying a user-defined function to create a corresponding output.
The operator may receive multiple messages with the same timestamp
(and messages with different timestamps may be delivered out of order).
A timing-message (an invocation of method \texttt{OnNotify}) indicates that
no more input messages with a timestamp $t$ will be subsequently delivered.
At this point, the operator completes the processing for time window $t$ and sends
a corresponding output message to its successor.

@@

The goal of this work is an automatic (memory-safe) region-based memory management technique
that supports dynamic regions (that are first-class objects) and higher-order functions.
Though our focus is on memory-safety, dynamic regions also have other side-benefits.
When a producer transfers a data-structure to a consumer, in a shared-memory context , our approach
provides an ownership discipline that ensures that the producer cannot subsequently modify
the data-structure. When the same transfer happens in a distributed setting, the system guarantees
that the data-structure is self-contained and can be safely transmitted across address spaces.

@@

The rest of the paper is organized as follows. The next section
presents an informal overview of \name, and motivates the need for a
region type system.  \S~\ref{sec:type-system} formalizes the type
system and its safety guarantees. The type inference algorithm is
described in \S~\ref{sec:type-inference}. \S~\ref{sec:csolve} focuses
on \csolve, the constraint solving algorithm, and its correctness
guarantees.  Implementations details and practical extensions to the
type system are described in \S~\ref{sec:implementation}.
\S~\ref{sec:evaluation} presents experimental evaluation and case
studies.  \S~\ref{sec:related} discusses the related work, and
\S~\ref{sec:conclusion} concludes.

>>>>

\newcommand{\TODO}[1]{\textbf{TODO: #1}}
\newcommand{\eg}{\emph{e.g.}}
\newcommand{\ie}{\emph{i.e.}}

@@

Consider the example, from~\cite{Broom:HotOS}, shown in Fig.~\ref{fig:motivating-eg}.
This code represents the logic for a streaming query operator.
The operator receives a stream of input messages, each associated
with a time (window) $t$, processed by method \texttt{onReceive}.
Each input message contains a list of inputs, each of which is processed
by applying a user-defined function to create a corresponding output.
The operator may receive multiple messages with the same timestamp
(and messages with different timestamps may be delivered out of order).
A timing-message (an invocation of method \texttt{OnNotify}) indicates that
no more input messages with a timestamp $t$ will be subsequently delivered.
At this point, the operator completes the processing for time window $t$ and sends
a corresponding output message to its successor.

@@

The goal of this work is a \emph{memory-safe} region-based memory management technique
that supports dynamic regions (that are first-class objects) and higher-order functions.
Though our focus, in this paper, is on memory-safety, our approach offers other side-benefits.
When a producer transfers a data-structure to a consumer, in a shared-memory context , our approach
provides an ownership discipline that ensures that the producer cannot subsequently modify
the data-structure. When the same transfer happens in a distributed setting, the system guarantees
that the data-structure is self-contained and can be safely transmitted across address spaces.
We refer to dynamic regions that provide these guarantees as \emph{transferable} regions.

@@

%The rest of the paper is organized as follows. The next section
%presents an informal overview of \name, and motivates the need for a
%region type system.  \S~\ref{sec:type-system} formalizes the type
%system and its safety guarantees. The type inference algorithm is
%described in \S~\ref{sec:type-inference}. \S~\ref{sec:csolve} focuses
%on \csolve, the constraint solving algorithm, and its correctness
%guarantees.  Implementations details and practical extensions to the
%type system are described in \S~\ref{sec:implementation}.
%\S~\ref{sec:evaluation} presents experimental evaluation and case
%studies.  \S~\ref{sec:related} discusses the related work, and
%\S~\ref{sec:conclusion} concludes.
